### 2016-03-23 docs/ms_communitySynchrony.Rmd
SI tex with good tables; updates SI table ref in main text

\textbf{Number of Tables and Figures}:  3 Tables;  3 Figures

@@

Across the five communities, our limiting case predictions closely matched synchrony from the corresponding simulation experiment (Table S1).
The correlation between our analytical predictions and simulated synchrony was 0.97 for $\phi_{R,\mathcal{M}_D}$ and 0.997 for $\phi_{R,\mathcal{M}_E}$.
The largest difference between predicted and simulated synchrony was 0.05 in New Mexico for $\phi_{R,\mathcal{M}_D}$ (Table 3).

@@

DISCUSSION
----------
Our study produced four main findings that were generally consistent across five natural plant communities: (1) limiting-case predictions from the theoretical model were well-supported by simulations from the empirical models; (2) demographic stochasticity decreased community synchrony, as expected by theory, and its effect was largest in small populations; (3) environmental fluctuations increased community synchrony relative to simulations in constant environments because species-specific responses to the environment were positively, though not perfectly, correlated; and (4) interspecific interactions were weak and therefore had little impact on community synchrony.
We also found that analyses based on synchrony of species' percent cover were uninformative (Online Supporting Information), implying that it is difficult to decipher mechanisms of species synchrony from abundance time series, as expected by theory [@Loreau2008a].

@@

In the Idaho community, removing environmental fluctuations did not cause a large decrease in synchrony.
However, that result appears to be an artifact. Removing environmental variation results in a negative invasion growth rate for *A. tripartita*. Although we only analyzed IBM runs in which *A. tripartita* had not yet gone extinct, it was at much lower abundance than in the other simulation runs.
When we removed *A. tripartita* from all simulations, the Idaho results conformed with results from all other sites: removing environmental stochasticity caused a significant reduction in species synchrony (Fig. S4).
Our main results for Idaho (Fig. 2), with *A. tripartita* included, demonstrate how the processes that determine species synchrony interact in complex ways.
*A. tripartita* has a facilitative effect on each grass species across all vital rates, except for a small competitive effect on *H. comata*'s survival probability (Tables S4, S9, S14).
At the same time, all the perennial grasses have negative effects on each other for each vital rate (Tables S4, S9, S14).
We know synchrony is affected by interspecific competition [@Loreau2008a], but how facilitative effects manifest themselves is unknown.
The interaction of facilitation and competition is clearly capable of having a large effect on species synchrony, and future theoretical efforts should aim to include a wider range of species interactions.

>>>>

\textbf{Number of Tables and Figures}:  2 Tables;  3 Figures

@@

Across the five communities, our limiting case predictions closely matched synchrony from the corresponding simulation experiment (Fig. 1 and Table S1).
The correlation between our analytical predictions and simulated synchrony was 0.97 for $\phi_{R,\mathcal{M}_D}$ and 0.997 for $\phi_{R,\mathcal{M}_E}$.
The largest difference between predicted and simulated synchrony was 0.05 in New Mexico for $\phi_{R,\mathcal{M}_D}$ (Table S1).

@@

DISCUSSION
----------
Our study produced four main findings that were generally consistent across five natural plant communities: (1) limiting-case predictions from the theoretical model were well-supported by simulations from the empirical models; (2) demographic stochasticity decreased community synchrony, as expected by theory, and its effect was largest in small populations; (3) environmental fluctuations increased community synchrony relative to simulations in constant environments because species-specific responses to the environment were positively, though not perfectly, correlated; and (4) interspecific interactions were weak and therefore had little impact on community synchrony.
We also found that analyses based on synchrony of species' percent cover were uninformative (Figs. S2-S3), implying that it is difficult to decipher mechanisms of species synchrony from abundance time series, as expected by theory [@Loreau2008a].

@@

In the Idaho community, removing environmental fluctuations did not cause a large decrease in synchrony.
However, that result appears to be an artifact. 
Removing environmental variation results in a negative invasion growth rate for *A. tripartita*. 
Although we only analyzed IBM runs in which *A. tripartita* had not yet gone extinct, it was at much lower abundance than in the other simulation runs.
When we removed *A. tripartita* from all simulations, the Idaho results conformed with results from all other sites: removing environmental stochasticity caused a significant reduction in species synchrony (Fig. S4).
Our main results for Idaho (Fig. 2), with *A. tripartita* included, demonstrate how the processes that determine species synchrony interact in complex ways.
*A. tripartita* has a facilitative effect on each grass species across all vital rates, except for a small competitive effect on *H. comata*'s survival probability (Tables S8-S10).
At the same time, all the perennial grasses have negative effects on each other for each vital rate (Tables S8-S10).
We know synchrony is affected by interspecific competition [@Loreau2008a], but how facilitative effects manifest themselves is unknown.
The interaction of facilitation and competition is clearly capable of having a large effect on species synchrony, and future theoretical efforts should aim to include a wider range of species interactions.

### 2016-03-23 docs/online_supporting_information.tex
SI tex with good tables; updates SI table ref in main text

\begin{table}[ht]
\centering
\caption{Average interaction coefficients across vital rates for each community.} 
\begin{tabular}{lrr}
  \hline
site & Interspecific Competition & Intraspecific Competition \\ 
  \hline
Arizona & -0.17 & -0.64 \\ 
  Idaho & -0.04 & -0.71 \\ 
  Kansas & 0.02 & -0.35 \\ 
  Montana & 0.04 & -0.98 \\ 
  NewMexico & -0.12 & -0.62 \\ 
   \hline
\end{tabular}
\end{table}

>>>>

\begin{table}[ht]
\centering
\caption{Average interaction coefficients for each vital rate for each community.} 
\begin{tabular}{llrrr}
  \hline
Site & Interaction Type & Growth & Recruitment & Survival \\ 
  \hline
Arizona & Interspecific & -0.0111 & -0.4430 & -0.0508 \\ 
  Arizona & Intraspecific & -0.0402 & -1.4271 & -0.4446 \\ 
  Idaho & Interspecific & 0.0022 & -0.1156 & 0.0059 \\ 
  Idaho & Intraspecific & -0.0469 & -1.5581 & -0.5269 \\ 
  Kansas & Interspecific & -0.0008 & 0.0509 & -0.0041 \\ 
  Kansas & Intraspecific & -0.0062 & -0.9916 & -0.0587 \\ 
  Montana & Interspecific & -0.0053 & 0.0922 & 0.0354 \\ 
  Montana & Intraspecific & -0.0733 & -2.0499 & -0.8105 \\ 
  NewMexico & Interspecific & -0.0027 & -0.3441 & -0.0080 \\ 
  NewMexico & Intraspecific & -0.0111 & -1.6425 & -0.2191 \\ 
   \hline
\end{tabular}
\end{table}
